\section*{Schauder Theory}
\subsection*{Schauder Estimates}

\begin{theorem}[Global $C^{2,\alpha}$-Estimate]
	\label{thm:gSe}
	Let $\Omega \subseteq \subseteq \mathbb{R}^n$ of class $C^{2,\alpha}$, $0 < \alpha < 1$. Moreover, let $a^{ij} \in C^{1,\alpha}(\Omega)$ symmetric, uniformly elliptic and uniformly bounded, $c \in C^\alpha(\Omega)$, $u_0 \in C^{2,\alpha}(\wbar{\Omega})$, $f = (f^1,\dots,f^n) \in C^{1,\alpha}(\Omega)$ and $h \in C^{\alpha}(\Omega)$. Then any solution $u \in C^{2,\alpha}(\Omega)$ of the Dirichlet boundary value problem
	\begin{align*}
		\ccases{
			A_0u + cu = -\frac{\partial}{\partial x^i} f^i + h & \text{in } \Omega,\\
			u = u_0 & \text{on } \Omega
		}
	\end{align*}
	\noindent satisfies
	\begin{equation*}
		\norm{u}_{C^{2,\alpha}} \leq C(\norm{u}_{H^1} + \norm{f}_{C^{1,\alpha}} + \norm{h}_{C^\alpha} + \norm{u_0}_{C^{2,\alpha}})
	\end{equation*}
	\noindent where $C$ does not depend on $u$.
\end{theorem}

\subsection*{Existence Theorems}

\begin{proposition}[Method of Continuity]
	\label{pro:moc}
	Let $(X,\norm{\cdot}_X)$ and $(Y,\norm{\cdot}_Y)$ be Banach spaces. Given $A_0,A_1 \in \mathcal{L}(X,Y)$ define $A_t := (1 - t)A_0 + tA_1$, $t \in \intcc{0,1}$. Suppose that
	\begin{equation*}
		\exists C > 0\forall t \in \intcc{0,1}\forall x \in X:\> \norm{x}_X \leq \norm{A_t x}_Y.
	\end{equation*}
	\noindent Then $A_0$ is surjective if and only if $A_1$ is surjective.
\end{proposition}

Using the method of continuity \ref{pro:moc}, one can show existence results of solutions of Dircihlet boundary value problems. Define
\begin{equation*}
	A_0 := - \frac{\partial}{\partial x^i}\del[3]{a^{ij}\frac{\partial}{\partial x^j}}
\end{equation*}
\noindent for $a^{ij} \in C^{1,\alpha}$ symmetric, uniformly elliptic and uniformly bounded. Consider the problem
\begin{align*}
	\ccases{
		A_0u + cu = -\frac{\partial}{\partial x^j}f^i + h & \text{in } \Omega,\\
		u = u_0 & \text{on } \partial \Omega
	}
\end{align*}
\noindent for $c \in C^\alpha$, $f = (f^1,\dots,f^n) \in C^{1,\alpha}$ and $h \in C^\alpha$. If $c \geq 0$, one can show existence and uniqueness of $C^{2,\alpha}$ solutions. First of all, suppose that solutions of 
\begin{align*}
	\ccases{
		A_0u = h & \text{in } \Omega,\\
		u = 0 & \text{on } \partial \Omega
	}
\end{align*}
\noindent do exist. Let us define
\begin{equation*}
	X := \cbr[0]{u \in C^{2,\alpha} : u\vert_{\partial \Omega} = 0} \qquad \text{and} \qquad Y := C^\alpha.
\end{equation*}
Then $X$ and $Y$ are Banach spaces, since $X$ is a closed subset of a Banach space. Define now $A_1 := A_0 + c$. Then it is easy to show that $A_0$ and $A_1$ are continuous. Thus to apply the continuity method, we have to show the existence of a constant $C > 0$, such that for all $t \in \intcc{0,1}$ and $u \in X$
\begin{equation*}
	\norm{x}_{C^{2,\alpha}} \leq \norm{A_t x}_{C^\alpha}
\end{equation*}
\noindent holds. But this looks like the $C^{2,\alpha}$-estimate \ref{thm:gSe}. Indeed, since $u \in C^{2,\alpha}$ solves $A_t u = A_tu$, we get
\begin{equation*}
	\norm{u}_{C^{2,\alpha}} \leq C(\norm{u}_{H^1} + \norm[0]{A_tu}_{C^\alpha}).
\end{equation*}
Using ellipticity, integration by parts (justified since any fucntion in $X$ vanishes on the boundary $\partial \Omega$) and $c \geq 0$, we compute
\begin{align*}
	\lambda\norm{u}_{H^1}^2 &= \lambda\int_{\Omega}\abs[0]{\nabla u}^2\\
	&\leq \int_{\Omega} a^{ij} \frac{\partial u}{\partial x^i}\frac{\partial u}{\partial x^j}\\
	&= \int_\Omega (A_0u)u\\
	&= \int_\Omega (A_0u)u + ctu^2 - ctu^2\\
	&= \int_\Omega (A_tu)u - ctu^2\\
	&\leq \int_\Omega (A_tu)u\\
	&\leq \norm{A_tu}_{L^2}\norm{u}_{L^2}\\
	&\leq C\norm{A_tu}_{C^\alpha}\norm{u}_{H^1}.
\end{align*}

